Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-23 article.Rmd
Fix typo in penultimate sentence

A major advantage of the approach is that it is scalable.
It would be feasible to internationalise the approach, given sufficient computer and developer resource to overcome the key data barriers: lack to cycling potential data and lack of road width data that are specific to the UK.
<!-- Given the recent interest in and funding for pop-up cycleways, projects inspired by and building on the work presented in this paper, can help ensure that pop-up cycleway plans are evidence-based and effective, maximising the chances of them becoming permanent. -->
In summary, the methods presented can help lock-in the benefits of COVID-19 related cycling booms long term.

>>>>

A major advantage of the approach is that it is scalable.
It would be feasible to internationalise the approach, given sufficient computer and developer resource to overcome the key data barriers: lack of cycling potential and road width data.
<!-- Given the recent interest in and funding for pop-up cycleways, projects inspired by and building on the work presented in this paper, can help ensure that pop-up cycleway plans are evidence-based and effective, maximising the chances of them becoming permanent. -->
In summary, the methods presented can help lock-in the benefits of COVID-19 related cycling booms long term.
